Higher-Order unification for free!

### 2024-04-10 paper/main.tex
todo

\paragraph{Decompilation}
During \elpiIn{progress}, as claimed in \cref{inv:beta-rhs}, the decompilation
can only have \linkbeta with not instantiated \lhs. In this case, \lhs is
unified with \rhs.
\noteD[inline]{not really sure of this, we can have $F\appsep a = \lambda x.G x$.
In this case when do we fail: for sure in decompile. But to respect fidelity,
we should fail immediately: we have a \linkbeta and a \linketa with same \lhs}

>>>>

\paragraph{Decompilation}
During \elpiIn{progress}, as claimed in \fullref{inv:beta-rhs}, the decompilation
can only have \linkbeta with not instantiated \lhs. In this case, \lhs is
unified with \rhs.
\todo{qui falliamo, nella 7.3 dire che LHS è in llambda quindi LSH = Ugly può funzionare,
in Elpi funziona però in questi casi il termine in llam deve essere a sinistra}.
